Data Preparation

### 2019-01-10 Data Preparation.Rmd
text AoD

#### AoD from ILOs
In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  unique

@@

#### AoD from Assessment

In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
```{r map_assessment_AoD}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers. In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`. Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

@@

### Courses
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))

d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code")

rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
print(d_course_detail)
```

```{r join d_course_detail}
d_course <- full_join(d_course, d_course_detail, by = "Code") %>%
  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())

rm(d_course_detail)
print(d_course)
```

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
d_course <- d_course %>%
  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
                                  Code == "UGR3002" ~ "UGR2002",
                                  Code == "UGR3003" ~ "UGR2003",
                                  Code == "UGR3005" ~ "UGR2005")))

@@

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    `Missing from ILO File` = as.logical(`Missing from ILO File`),
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))
print(select(d_course, Code, Letters, Number, Level))
```

>>>>

#### AoD from ILOs
(For this section we use: `d_ILO`-indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD)

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  unique

@@

#### AoD from Assessment
(For this section we use: `d_assessment`-indicates which type(s) of assessment each course contains with one row per course-assessment)

In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.

```{r map_assessment_AoD}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract the row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

@@

### Courses
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  unique %>%
  count(Code) %>%
  rename(n_ILO = n)
print(d_ILO_detail)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))
print(d_assessment_detail)

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))
print(d_AoD_detail)
```

```{r}
d_course <- d_course %>%
  full_join(d_ILO_detail       , by = "Code") %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code") %>%
  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
print(d_course)
```

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r}
d_course <- d_course %>%
  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
                                  Code == "UGR3002" ~ "UGR2002",
                                  Code == "UGR3003" ~ "UGR2003",
                                  Code == "UGR3005" ~ "UGR2005")))

@@

Finally, we add a series of informative variable at the course level.
```{r}
d_course <- d_course %>%
  mutate(
    `Missing from ILO File` = as.logical(`Missing from ILO File`),
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))
print(select(d_course, Code, Letters, Number, Level))
```
